\bf The Left Arm Bias in ITF Taekwon-Do Patterns \\ Chon-Ji to Juche

### 2011-02-25 article.tex
Added content to techniques by motion type

  % all techniques by height
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/height_all}
    \caption{All techniques by height}
    \label{fig:height_all}
  \end{figure}

  Techniques by height follow the same trend when looking at all techniques
  combined or techniques to either side. In general, there are more blocks
  than any other technique. Most of the techniques are in the middle section,
  although there is a greater occurrence of strikes in the high section, and
  very few attacks in the low section.

\SubSection{Techniques by Patterns}

  % all techniques by patterns
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_all}
    \caption{All techniques by patterns}
    \label{fig:patterns_all}
  \end{figure}

  % left techniques by patterns
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_left}
    \caption{Left techniques by patterns}
    \label{fig:patterns_left}
  \end{figure}

  % right techniques by patterns
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_right}
    \caption{Right techniques by patterns}
    \label{fig:patterns_right}
  \end{figure}

\clearpage

  % all techniques by black belt patterns
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_all}
    \caption{All techniques by black belt patterns}
    \label{fig:patterns_black_all}
  \end{figure}

  % left techniques by black belt patterns
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_left}
    \caption{Left techniques by black belt patterns}
    \label{fig:patterns_black_left}
  \end{figure}

  % right techniques by black belt patterns
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_right}
    \caption{Right techniques by black belt patterns}
    \label{fig:patterns_black_right}
  \end{figure}

  % all techniques by color belt patterns
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_all}
    \caption{All techniques by color belt patterns}
    \label{fig:patterns_color_all}
  \end{figure}

  % left techniques by color belt patterns
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_left}
    \caption{Left techniques by color belt patterns}
    \label{fig:patterns_color_left}
  \end{figure}

  % right techniques by color belt patterns
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_right}
    \caption{Right techniques by color belt patterns}
    \label{fig:patterns_color_right}
  \end{figure}

@@

  % All techniques by stances
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/stances_all}
    \caption{All techniques by stances}
    \label{fig:stances_all}
  \end{figure}

  % Left techniques by stances
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/stances_left}
    \caption{Left techniques by stances}
    \label{fig:stances_left}
  \end{figure}

  % Right techniques by stances
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/stances_right}
    \caption{Right techniques by stances}
    \label{fig:stances_right}
  \end{figure}

  % All techniques by stances except walking, sitting and L
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/stances_not_wsl}
    \caption{All techniques by stances except walking, sitting and L}
    \label{fig:stances_not_wsl}
  \end{figure}

  % Left techniques by stances except walking, sitting and L
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/stances_left_not_wsl}
    \caption{Left techniques by stances except walking, sitting and L}
    \label{fig:stances_left_not_wsl}
  \end{figure}

  % Right techniques by stances except walking, sitting and L
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/stances_right_not_wsl}
    \caption{Right techniques by stances except walking, sitting and L}
    \label{fig:stances_right_not_wsl}
  \end{figure}

@@

  % all techniques by motion type
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/motion_all}
    \caption{All techniques by all motion types}
    \label{fig:motion_all}
  \end{figure}

  Most techniques are normal motion, followed by fast motion and continuous
  motion.

  There are more motion types on the right side, than on the left. Right side
  has flying motion and consecutive motion, whereas the left side does not.
  There are more flying, slow, sliding and consecutive motions on the right
  side. On the left side, there are more fast, stamping continuous and
  connecting motions than on the right side.

  There are equal amounts of slow, jumping, dodging, double stepping, shifting
  motions on both sides, although with different groups of techniques.

  % all techniques by motion type except normal motion
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/motion_all_not_n}
    \caption{All techniques by motion type except normal motion}
    \label{fig:motion_all_not_n}
  \end{figure}

  % left techniques by motion type except normal motion
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/motion_left_not_n}
    \caption{Left techniques by motion type except normal motion}
    \label{fig:motion_left_not_n}
  \end{figure}

  % right techniques by motion type except normal motion
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/motion_right_not_n}
    \caption{Right techniques by motion type except normal motion}
    \label{fig:motion_right_not_n}
  \end{figure}

>>>>

  % all techniques by height
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/height_all}
    \caption{All techniques by height.}
    \label{fig:height_all}
  \end{figure}

  Techniques by height follow the same trend when looking at all techniques
  combined or techniques to either side (Figure \ref{fig:height_all}). In
  general, there are more blocks than any other technique. Most of the
  techniques are in the middle section, although there is a greater occurrence
  of strikes in the high section, and very few attacks in the low section.

@@

  % All techniques by Walking, Sitting and L stances
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/stances_all}
    \caption{All techniques by walking, sitting and L stances.}
    \label{fig:stances_all}
  \end{figure}

  Because most techniques are performed in walking, sitting and L stances, the
  graphs in this section have been split into two groups. One group shows the
  majority of techniques (84 \%), while the other visualize techniques in
  every other stance (16 \%).

  When looking at all techniques by walking stances, sitting stances and L
  stances (Figure \ref{fig:stances_all}), they roughly follow the same pattern
  on both sides. There are, however, two minor exceptions. Firstly, there are
  more strikes in L stances compared to walking stances on the left side.
  Secondly, there are more punches than blocks to the right side.

  % TODO All techniques by stances except walking, sitting and L stances
  % show all techniques with *all* stances?

  % All techniques by stances except walking, sitting and L stances
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/stances_not_wsl}
    \caption{All techniques by stances except walking, sitting and L stances.}
    \label{fig:stances_not_wsl}
  \end{figure}

  % Left techniques by stances except walking, sitting and L
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/stances_left_not_wsl}
    \caption{Left techniques by stances except walking, sitting and L stances.}
    \label{fig:stances_left_not_wsl}
  \end{figure}

  % Right techniques by stances except walking, sitting and L
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/stances_right_not_wsl}
    \caption{Right techniques by stances except walking, sitting and L
    stances.}
    \label{fig:stances_right_not_wsl}
  \end{figure}

@@

  % all techniques by motion type
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/motion_all}
    \caption{All techniques by all motion types.}
    \label{fig:motion_all}
  \end{figure}

  There are 14 different motion types registered in our data set. The larger
  part of techniques (76 \%) are performed in normal motion (Figure
  \ref{fig:motion_all}), followed by continuous motion (6 \%) and fast motion
  (4 \%).

  % all techniques by motion type except normal motion
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/motion_all_not_n}
    \caption{All techniques by motion type except normal motion.}
    \label{fig:motion_all_not_n}
  \end{figure}

  Excluding normal motion, it is interesting to note the high presence of
  blocks in continuous motion, which alone amounts to 34 \% of blocks
  performed (Figure \ref{fig:motion_all_not_n}). Continuing with Figure
  \ref{fig:motion_all_not_n}, it shows that there is an abnormal number of
  punches performed in fast motion compared to other motion types.

  % left techniques by motion type except normal motion
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/motion_left_not_n}
    \caption{Left techniques by motion type except normal motion.}
    \label{fig:motion_left_not_n}
  \end{figure}

  % right techniques by motion type except normal motion
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/motion_right_not_n}
    \caption{Right techniques by motion type except normal motion.}
    \label{fig:motion_right_not_n}
  \end{figure}

  When examining the number of different motion types to either side, we find
  that there are more motion types on the right side, than on the left. The
  right side has flying motion and consecutive motion, in additon to motion
  types found on the left side. Also, there are more flying, slow, sliding and
  consecutive motions on the right side. However, there are more fast,
  stamping, continuous and connecting motions on the left side. Comparing the
  number of motion types on both sides reveals that there are equal amounts of
  slow, jumping, dodging, double stepping and shifting motions, although with
  different groups of techniques (Figures \ref{fig:motion_left_not_n},
  \ref{fig:motion_right_not_n}.

%\SubSection{Techniques by Patterns}

  %% all techniques by patterns
  %\begin{figure}
    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_all}
    %\caption{All techniques by patterns.}
    %\label{fig:patterns_all}
  %\end{figure}

  %% left techniques by patterns
  %\begin{figure}
    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_left}
    %\caption{Left techniques by patterns.}
    %\label{fig:patterns_left}
  %\end{figure}

  %% right techniques by patterns
  %\begin{figure}
    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_right}
    %\caption{Right techniques by patterns.}
    %\label{fig:patterns_right}
  %\end{figure}

  %% all techniques by black belt patterns
  %\begin{figure}
    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_all}
    %\caption{All techniques by black belt patterns.}
    %\label{fig:patterns_black_all}
  %\end{figure}

  %% left techniques by black belt patterns
  %\begin{figure}
    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_left}
    %\caption{Left techniques by black belt patterns.}
    %\label{fig:patterns_black_left}
  %\end{figure}

  %% right techniques by black belt patterns
  %\begin{figure}
    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_right}
    %\caption{Right techniques by black belt patterns.}
    %\label{fig:patterns_black_right}
  %\end{figure}

  %% all techniques by color belt patterns
  %\begin{figure}
    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_all}
    %\caption{All techniques by color belt patterns.}
    %\label{fig:patterns_color_all}
  %\end{figure}

  %% left techniques by color belt patterns
  %\begin{figure}
    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_left}
    %\caption{Left techniques by color belt patterns.}
    %\label{fig:patterns_color_left}
  %\end{figure}

  %% right techniques by color belt patterns
  %\begin{figure}
    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_right}
    %\caption{Right techniques by color belt patterns.}
    %\label{fig:patterns_color_right}
  %\end{figure}
